Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-25 main.Rmd
CONTENT CUT - DATA STRUCTURE - iteration 1

For more variations of calendar algrabra operations, see @Ning2002-tf.

@@

Periodic and Quasi-periodic behavior can be defined by a repeating pattern, except for a finite number of granules that can be seen as discontinuity points in the granularity in case of quasi-periodic behavior. Aperiodic time granularities are the ones which can not be specified as a periodic repetition of a pattern of granules. Most public holidays repeat every year, but there is no finite (or reasonably small) period within which their behavior remains constant. A classic example can be that of Easter, whose dates repeat only after 5,700,000 years. U.S labour day is the first Monday in September and U.S. Memorial Day is the last day in May. In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend. Examples of aperiodic granularity may also include school holidays or a scheduling event that might cover the first and third Monday of the month between June and October, except for state holidays. All of these are recurring events, but with non-periodic patterns. As such, plausible $P_i$ from \autoref{tab:quasi} could be possibly infinite for aperiodic granularities.

@@

**Discussion**: Here, $M_1$ can be an aperiodic linear granularity denoting block leaves during Christmas, $M_2$ can be the one denoting Easter, $M_n$ can be Labour day and M can be conceived as the aperiodic linear granularity denoting any holidays. The number of categories obtained coincides with the number of aperiodic linear granularities considered and an additional category representing no event.

@@

Generally speaking, to keep it simple, we consider the case of only one quasi-circular single order-up granularity in the hierarchy table. Any multiple order-up quasi-circular granularity $C_{l, m}(z)$ can then be considered to be a function of two single order-up granularities $C_{l,m'}(z)$ and $C_{m',m}(z)$. Two different approaches need to be employed for the follwing cases:

@@

Effective exploration or good visualization require good data structures. It is recognized that there is a crucial influence of linear vs cyclic time characteristics on the expressiveness of visualization and analysis. Moreover, one can use calendars based on application domain that define contextual system of linear and cyclic granularities. However, restructuring time in this manner leads to re-organisation of the data structure, where each level of a cyclic granularity correspond to multiple values of the measured variable, unlike the case of linear granularities where each time point corresponds to an unique value of the measured variable. It is common to see consolidation of these multiple values through aggregation or an unique summary statistic like mean or median to have each level of cyclic granularity to correspond to an unique value of the measured variable. But that approach  hides the distributions of the measured variable induced by the re-organised data structure. Summarizing the probability distribution of these multiple observations using some summary statistics together, each of which can highlight different properties of the data could be a potential way to compehend periocities in the data. Hence, a possible data structure would be to consider different summarisation of the probability distribution of the measured variable across two cyclic granularities. Any attempt to encode all or many cyclic granularities at the same time to develop insights on periodicity might become clumsy. Instead, the big problem is broken down into smaller pieces by focusing on two cyclic granularities at a time.

@@

The way cyclic granularities relate become important when we consider the data structure in Figure \@ref(fig:data-structure). While considering data sets of the form $<C_1, C_2, v>$, let $S_{ij}$ be the set of index set such that for all $s \in S_{ij}$, $C_1(s) = A_i$ and $C_2(s) = B_j$. Data subsets like <$A_i$, $B_j$, $v(s)$> can be obtained for all $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$  which will lead to $nm$ data subsets. We will discuss few cases, where one or more of these $nm$ sets will be empty, the implication of which we will discuss in Section \ref{sec:vis-interaction}.

@@

Firstly, empty combinations can arise due to the structure of the calendar or hierarchy.
These are "structurally" empty combinations in that it is impossible for them to have any value of the measured variable. Let us take a specific example, where $C_1$ be day-of-month and $C_2$ be week-of-month. Here $C_1$ can have 31 levels/categories while $C_2$ can have 5 categories. There will be $31\times 5=155$ sets $S_{ij}$ corresponding to the possible combinations of day-of-month and week-of-month. Many of these are empty. For example $S_{1,5}$, $S_{21,2}$, etc. This is also intuitive since the first day of the month can never correspond to fifth week of the month.

@@

Secondly, empty combinations can turn up due to differences in event location or duration in a calendar. These are called "event-driven" empty combinations. Let us consider $C_1$ be day-of-week and $C_2$ be WorkingDay/NonWorkingDay. Here $C_1$ can have 7 levels while $C_2$ can have 2 levels. So there are 14 sets $S_{ij}$ corresponding to the possible combinations of $C_1$ and $C_2$. While potentially all of these can be non-empty (it is possible to have a public holiday on any day-of-week), in practice many of these combinations will probably have very few observations. For example, there are few (if any) public holidays on Wednesdays or Thursdays in any given year in Melbourne, Australia.

@@

Thirdly, empty combinations can be a result of how granularities are constructed. These are called "build-based" empty combinations. Let $C_1$ be Business-days, which are days from Monday to Friday except holidays and $C_2$ is day-of-month. Then the days denoting weekends in a month would not correspond to any Business days and would have missing observations due to the way the granularities are constructed. This is different from structurally empty combinations because structure of the calendar does not lead to these missing combinations, but the construction of the granularity does.

@@

If we assume that $X_1, X_2, \dots, X_n \sim F$ are independent and identically distributed observations from an univariate distribution with probability density/mass function $f(.)$ and $X_{(1)},\dots X_{(n)}$ denote the order statistics of $X_1, X_2, \dots, X_n$, the Kernel density estimator $\hat{f(x)}$ with Kernel $K$ is defined by:

\begin{equation}
\hat{f(x)} = (1/nh)\sum_{i=1}^{n} K(x-X_i)/h
\end{equation}

where $h$ is the smoothing parameter or the bandwidth. The MSE of the estimator is given by:

\begin{equation}\label{eq:MSE}
\begin{split}
MSE(\hat{q(u)}) & = (1/4)h^4(q''(u))^2 \sigma_k^4 + (1/nh)q^2(u) \kappa \\
\end{split}
\end{equation}

@@

<!-- where $Q(u)= F^{-1}(u) = inf({x: F(x) >u)}$, $0<u< 1$ and  $q \equiv  Q'$. -->
<!-- MSE(\hat{f(x)}) & = (1/4)h^4(f''(x))^2 \sigma_k^4 + (1/nh)f(x) \kappa -->

@@

<!-- A well designed visual representation can replace cognitive calculations with simple perpetual inferences and improve speed of comprehension and decision making. However, creating a visualisation requires a number of nuanced judgements. The challenge being given a data set, the number of visual encodings and hence the space of possible visual design is extremely huge.  -->

@@

Choice of plots are dictated by the statistical transformations and geometric objects used for the visualization. The basic plot choice for our data structure is the one that can display densities. In Section \ref{sec:measured-variable}, it is discussed that these densities could be estimated using Kernel density estimates or some descriptive statistics.
We will discuss few conventional and recent ways to plot distributions using both of these methods.

@@

Most commonly used displays include the box plots [@Tukey1977-jx] which convey statistical features such as the median, quartile boundaries, hinges, whiskers and extreme outliers.<!--These displays are based on descriptive statistics, for example, $([n/2] + 1)/2^{\text{th}}$ and $(n + 1 - ([n/2] + 1)/2)^{\text{th}}$ order statistics are taken as estimates of the quartiles.--> Due to wide spread popularity and simplicity in implementation, a number of variations are proposed which provides alternate definitions of quantiles, whiskers, fences and outliers. Notched box plots [@Mcgill1978-hg] has box widths proportional to the number of points in the group and display confidence interval around medians aims to overcome some drawbacks of box plots.<!-- Challenge of boxplot --> The standard box plot and all of it's variations are helpful to get an idea of the distribution at a glance. However, for data less than 1000 observations, detailed estimates of tail behavior beyond the quartiles are not trustworthy. Also, the number of outliers is large for larger data sets.

<!-- Description and lit review of letter-value plots -->
The letter-value box plot [@Hofmann2017-sg] was designed to adjust for number of outliers proportional to the data size and display more reliable estimates of tail and are particularly useful for large data sets. “outliers” in letter value plots are those observations beyond the most extreme letter value. The letter values are shown till the depths where the letter values are reliable estimates of their corresponding quantiles and hence might lead to a lot of letter values being shown, leading to overload of information in one plot.

@@

Quantile plots display quantiles instead of quartiles in a traditional boxplot. These plots give more information than box plots and yet avoid clutter by enabling us to focus just on specific probabilities. While in a boxplot, an outlier is defined as a data point that is located outside the fences (“whiskers”) of the boxplot (e.g. outside 1.5 times the interquartile range above the upper quartile and below the lower quartile), in quantile plots outliers are open to interpretation and not shown.

@@

Traditional ways to visualize kernel densities include violin plots [@Hintze1998-zi]. The shape of the violin represents the density estimate of the variable. The more data points in a specific range, the larger the violin is for that range. Adding two density plots gives a symmetric plot which makes it easier to see the magnitude of the density and compare across categories, enabling easier detection of clusters or bumps within a distribution. It becomes less useful when there are too many levels or categories to display.

The summary plot [@Potter2010-qc] combines a minimal box plot with glyphs representing the first five moments (mean, standard deviation, skewness, kurtosis and tailings), and a sectioned density plot crossed with a violin plot and an overlay of a reference distribution. This suffers from the same problem as boxplots or violin plot, as it is combination of those two.

<!-- Description and lit review of density plots -->
 A Ridge line plot (sometimes called Joy plot) shows the distribution for several groups. Distribution can be represented using density plots, all aligned to the same horizontal scale and presented with a slight overlap. Like other density based displays, these plots allow us to see multimodality in the distribution. However, these plots can be obscuring when there is overlap of distribution for two or more categories of the y-axis. Also, with lot of categories, it is difficult to compare the height of the densities across categories.

@@

Each type of density display has different parameters, that need to be estimated given the data. Each is equipped with some benefits and challenges. For example, if we have too many categories in the variables mapped to facet or x-axis, the quantile plots might be useful for comparing patterns, whereas, other more involved methods of plotting are useful for studying anomalies, outlier or multimodal behavior.

@@

We will discuss the effect of the levels of cyclic granularities in this section. Recall that cyclic granularities $C_1$ and $C_2$ are such that $C_1$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_n$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\}. $A_i$'s and $B_j$'s are referred to as the levels of $C_1$ and $C_2$ for all $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$ respectively. The levels have an impact on the choice of plots since space and resolution might become a problem if the number of levels are too high. A potential approach can be to categorize the levels as very high/high/medium/low for each cyclic granularities and define some criteria based on usual cognitive power, display size available and the aesthetic mappings. Default values for these categorizations can be chosen based on levels of common temporal granularities like days-of-month, days-of-fortnight and days-of-week. For example, any levels above 31 can be considered as very high, any levels between 14 to 31 can be taken as high and that between 7 to 14 can be taken as medium and below 7 as low.

@@

We will discuss the effect of the interaction of cyclic granularities in this section. In Section \ref{sec:synergy}, we discussed how pairs of granularities can have empty combinations either due to structure of calendar, event location or duration or due to the way they are built. In this section, we will see how these empty combinations affect the visualization when a dependent variable is plotted against these granularities.

For illustration, distribution of half-hourly electricity consumption of Victoria is plotted across different time granularities in each of the panel in
\autoref{fig:allFig}. \autoref{fig:allFig} (a) shows the letter value plot across days of the month faceted by months like January, March and December. \autoref{fig:allFig} (c) shows box plot  across days of the year by the 1st, 15th, 29th and 31st days of the month. \autoref{fig:allFig} (d) showing violin plot across days of the month faceted by week of the month. \autoref{fig:allFig} (e), variations across week of the year conditional on week of the month can be observed through a ridge plot and \autoref{fig:allFig} (f) shows decile plots across  day of the year and month of the year.

@@

We will discuss the effect of the mapping of cyclic granularities in this section. When we consider data sets of the form <$C_1$, $C_2$, $v$> with $C_1$ mapped to $x$ position and $C_2$ to facets $A_i$'s are placed in close proximity and each $B_j$ represent a group/facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, in this case $A_i$'s are compared against each other within each group. When $C_2$ is mapped to facets and $C_1$ is mapped to $x$ axis, comparisons would ideally happen across all $B_j$ within each $A_i$. Although the variables used in the layers are the same, the difference in mapping leads to emphasis of different behavior of the variables.

@@

Even when there are no rarely occuring events, number of observations might vary hugely within or across each facet. This might happen due to missing observations in the data or uneven locations of events in time domain. In such cases, the statistical transformations based on density or quantile estimates should be used with caution as sample size would directly affect both the variance and consequently the confidence interval of the estimators. \autoref{eq:MSE} shows that the variance of both $\hat{f(x)}$ and $\hat{q(u)}$ is a function of the sample size $n$.

@@

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure <$C1$ $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualisation. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

>>>>

For more variations of calendar algebra operations, see @Ning2002-tf.

@@

Periodic and Quasi-periodic behavior can be defined by a repeating pattern, except for a finite number of granules that can be seen as discontinuity points in the granularity in case of quasi-periodic behavior. Aperiodic time granularities are the ones which can not be specified as a periodic repetition of a pattern of granules. Most public holidays repeat every year, but there is no finite (or reasonably small) period within which their behavior remains constant. A classic example can be that of Easter, whose dates repeat only after 5,700,000 years. U.S labor day is the first Monday in September and U.S. Memorial Day is the last day in May. In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend. Examples of aperiodic granularity may also include school holidays or a scheduling event that might cover the first and third Monday of the month between June and October, except for state holidays. All of these are recurring events, but with non-periodic patterns. As such, plausible $P_i$ from \autoref{tab:quasi} could be possibly infinite for aperiodic granularities.

@@

**Discussion**: Here, $M_1$ can be an aperiodic linear granularity denoting block leaves during Christmas, $M_2$ can be the one denoting Easter, $M_n$ can be Lab our day and M can be conceived as the aperiodic linear granularity denoting any holidays. The number of categories obtained coincides with the number of aperiodic linear granularities considered and an additional category representing no event.

@@

Generally speaking, to keep it simple, we consider the case of only one quasi-circular single order-up granularity in the hierarchy table. Any multiple order-up quasi-circular granularity $C_{l, m}(z)$ can then be considered to be a function of two single order-up granularities $C_{l,m'}(z)$ and $C_{m',m}(z)$. Two different approaches need to be employed for the following cases:

@@

Effective exploration or good visualization require good data structures. It is recognized that there is a crucial influence of linear vs cyclic time characteristics on the expressiveness of visualization and analysis. Moreover, one can use calendars based on application domain that define contextual system of linear and cyclic granularities. However, restructuring time in this manner leads to re-organisation of the data structure, where each level of a cyclic granularity correspond to multiple values of the measured variable, unlike the case of linear granularities where each time point corresponds to an unique value of the measured variable. It is common to see consolidation of these multiple values through aggregation or an unique summary statistic like mean or median to have each level of cyclic granularity correspond to an unique value of the measured variable. But that approach  hides the distributions of the measured variable induced by the re-organised data structure. Summarizing the probability distribution of these multiple observations across cyclic granularities using some summary statistics together, each of which can highlight different features of the data could be a potential way to comprehend periocities in the data. Any attempt to encode all or many cyclic granularities together to develop insights on periodicity might become clumsy. Instead, the big problem is broken down by focusing on two cyclic granularities at a time.

@@

The way cyclic granularities relate become important when we consider the data structure in Figure \@ref(fig:data-structure). While considering data sets of the form $<C_1, C_2, v>$, let $S_{ij}$ be the set of index set such that for all $s \in S_{ij}$, $C_1(s) = A_i$ and $C_2(s) = B_j$. Data subsets for each combination of levels ($A_i$, $B_j$) like <$A_i$, $B_j$, $v(s)$> can be obtained for all $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$  which will lead to $nm$ data subsets. We will discuss few cases, where one or more of these $nm$ sets will be empty, the implication of which we will discuss in Section \ref{sec:vis-interaction}.

@@

Firstly, empty combinations can arise due to the structure of the calendar or hierarchy.
These are "structurally" empty combinations in that it is impossible for them to have any value of the measured variable. Let us take a specific example, where $C_1$ be day-of-month with 31 levels and $C_2$ be week-of-month with 5 levels. There will be $31\times 5=155$ sets $S_{ij}$ corresponding to the possible combinations of day-of-month and week-of-month. Many of these are empty. For example $S_{1,5}$, $S_{21,2}$, etc. This is also intuitive since the first day of the month can never correspond to fifth week of the month.

@@

Secondly, empty combinations can turn up due to differences in event location or duration in a calendar. These are called "event-driven" empty combinations. Let us consider $C_1$ be day-of-week with 7 levels and $C_2$ be WorkingDay/NonWorkingDay with 2 levels. While potentially all of these 14 sets $S_{ij}$ can be non-empty (it is possible to have a public holiday on any day-of-week), in practice many of these will probably have very few observations. For example, there are few (if any) public holidays on Wednesdays or Thursdays in any given year in Melbourne, Australia.

@@

Thirdly, empty combinations can be a result of how granularities are constructed. These are called "build-based" empty combinations. Let $C_1$ be Business-days, which are days from Monday to Friday except holidays and $C_2$ is day-of-month. Then the days denoting weekends in a month would not correspond to any Business days. This is different from structurally empty combinations because structure of the calendar does not lead to these missing combinations, but the construction of the granularity does.

@@

If we assume that $X_1, X_2, \dots, X_n \sim F$ are independent and identically distributed observations from an univariate distribution with probability density/mass function $f(.)$, <!--and $X_{(1)},\dots X_{(n)}$ denote the order statistics of $X_1, X_2, \dots, X_n$,--> the Kernel density estimator $\hat{f(x)}$ with Kernel $K$ is defined by $\hat{f(x)} = (1/nh)\sum_{i=1}^{n} K(x-X_i)/h$, where $h$ is the smoothing parameter or the bandwidth. The MSE of the estimator is given by:
\begin{equation}\label{eq:MSE}
\begin{split}
MSE(\hat{f(x)}) & = (1/4)h^4(f''(x))^2 \sigma_k^4 + (1/nh)f(x) \kappa
\end{split}
\end{equation}

@@

<!-- where $Q(u)= F^{-1}(u) = inf({x: F(x) >u)}$, $0<u< 1$ and  $q \equiv  Q'$. -->
<!--  -->
<!-- MSE(\hat{q(u)}) & = (1/4)h^4(q''(u))^2 \sigma_k^4 + (1/nh)q^2(u) \kappa \\ -->

@@

<!-- A well designed visual representation can replace cognitive calculations with simple perpetual inferences and improve speed of comprehension and decision making. However, creating a visualization requires a number of nuanced judgements. The challenge being given a data set, the number of visual encodings and hence the space of possible visual design is extremely huge.  -->

@@

Choice of plots are dictated by the statistical transformations and geometric objects used for the visualization. The basic plot choice for our data structure is the one that can display distributions<!--In Section \ref{sec:measured-variable}, it is discussed that these densities could be estimated.-->. We will discuss few conventional and recent ways to plot distributions using both Kernel density estimates and descriptive statistics.

@@

Most commonly used displays include the box plots [@Tukey1977-jx] which convey statistical features such as the median, quartile boundaries, hinges, whiskers and extreme outliers at a glance.<!--These displays are based on descriptive statistics, for example, $([n/2] + 1)/2^{\text{th}}$ and $(n + 1 - ([n/2] + 1)/2)^{\text{th}}$ order statistics are taken as estimates of the quartiles.--> Due to wide spread popularity and simplicity in implementation, a number of variations like Notched box plots [@Mcgill1978-hg] are proposed which provides alternate definitions of quantiles, whiskers, fences and outliers.<!--has box widths proportional to the number of points in the group and display confidence interval around medians aims to overcome some drawbacks of box plots.<!-- Challenge of boxplot. The standard box plot and all of it's variations are helpful to get an idea of the distribution at a glance. -->. However, for data less than 1000 observations, detailed estimates of tail behavior beyond the quartiles are not trustworthy. Also, the number of outliers is large for larger data sets.

<!-- Description and lit review of letter-value plots -->
The letter-value box plot [@Hofmann2017-sg] was designed to adjust for number of outliers proportional to the data size and display more reliable estimates of tail and are particularly useful for large data sets.<!--“outliers” in letter value plots are those observations beyond the most extreme letter value.--> The letter values are displayed till the depths where the letter values are reliable estimates of their corresponding quantiles and hence might lead to a lot of letter values being shown, leading to overload of information in one plot.

@@

Quantile plots display quantiles instead of quartiles in a traditional boxplot. These plots give more information than box plots and yet avoid clutter by enabling us to focus just on specific probabilities. While in a boxplot and letter value plots are well defined <!--an outlier is defined as a data point that is located outside the fences (“whiskers”) of the boxplot (e.g. outside 1.5 times the interquartile range above the upper quartile and below the lower quartile)-->, in quantile plots outliers are open to interpretation and not shown.

@@

Traditional ways to visualize kernel densities include violin plots [@Hintze1998-zi]. The shape of the violin represents the density estimate of the variable. <!--The more data points in a specific range, the larger the violin is for that range. -->Adding two density plots gives a symmetric plot which makes it easier to see the magnitude of the density and compare across categories, enabling easier detection of clusters or bumps within a distribution. It becomes less useful when there are too many levels or categories to display.

The summary plot [@Potter2010-qc] combines a minimal box plot with glyphs representing the first five moments and a sectioned density plot crossed with a violin plot and an overlay of a reference distribution. This suffers from the same problem as boxplots or violin plot, as it is combination of those two.

<!-- Description and lit review of density plots -->
 A Ridge line plot <!--(sometimes called Joy plot)--> shows the distribution for several groups. Distribution can be represented using density plots, all aligned to the same horizontal scale and presented with a slight overlap. Like other density based displays, these plots allow us to see multimodality in the distribution. However, these plots can be obscuring when there is overlap of distribution for two or more categories of the y-axis. Also, with lot of categories, it is difficult to compare the height of the densities across categories.

@@

Each type of density display has different parameters, that need to be estimated given the data. Each is equipped with some benefits and challenges which should be borne in mind while using them for exploration. <!--For example, if we have too many categories in the variables mapped to facet or x-axis, the quantile plots might be useful for comparing patterns, whereas, other more involved methods of plotting are useful for studying anomalies, outlier or multimodal behavior-->

@@

We will discuss the effect of the levels of cyclic granularities on the choice of plots <!--Recall that for cyclic granularities $C_1$ and $C_2$ such that $C_1$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_n$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\}. $A_i$'s and $B_j$'s are referred to as the levels of $C_1$ and $C_2$ for all $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$ respectively.The levels have an impact on the--> since space and resolution might become a problem if the number of levels are too high. A potential approach could be to categorize the levels as very high/high/medium/low for each cyclic granularity and define some criteria based on usual cognitive power, display size available and the aesthetic mappings. Default values for these categorizations can be chosen based on levels of common temporal granularities like days-of-month, days-of-fortnight and days-of-week.<!--For example, any levels above 31 can be considered as very high, any levels between 14 to 31 can be taken as high and that between 7 to 14 can be taken as medium and below 7 as low.>

@@

We will discuss the effect of the interaction of cyclic granularities in this section.<!--In Section \ref{sec:synergy}, we discussed how pairs of granularities can have empty combinations either due to structure of calendar, event location or duration or due to the way they are built. In this section, we will see how these empty combinations affect the visualization when a dependent variable is plotted against these granularities.--> For illustration, distribution of half-hourly electricity consumption of Victoria is plotted across different time granularities in each of the panel in
\autoref{fig:allFig}. \autoref{fig:allFig} (a) shows the letter value plot across days of the month faceted by months like January, March and December. \autoref{fig:allFig} (c) shows box plot  across days of the year by the 1st, 15th, 29th and 31st days of the month. \autoref{fig:allFig} (d) showing violin plot across days of the month faceted by week of the month. \autoref{fig:allFig} (e), variations across week of the year conditional on week of the month can be observed through a ridge plot and \autoref{fig:allFig} (f) shows decile plots across  day of the year and month of the year.

@@

We will discuss the effect of the mapping of cyclic granularities in this section. When we consider data sets of the form <$C_1$, $C_2$, $v$> with $C_1$ mapped to $x$ position and $C_2$ to facets $A_i$'s are placed in close proximity and each $B_j$ represent a group/facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, in this case $A_i$'s are compared against each other within each group.<!-- When $C_2$ is mapped to facets and $C_1$ is mapped to $x$ axis, comparisons would ideally happen across all $B_j$ within each $A_i$-->. With the mapping of $C1$ and $C_2$ reversed, emphasis will shift to different behavior of the variables.

@@

Even when there are no rarely occuring events, number of observations might vary hugely within or across each facet. This might happen due to missing observations in the data or uneven locations of events in time domain. In such cases, the statistical transformations based on density should be used with caution as sample sizes would directly affect both the variance and consequently the confidence interval of the estimators (see \autoref{eq:MSE})

<!--  shows that the variance of both $\hat{f(x)}$ <!--and $\hat{q(u)}$--> is a function of the sample size $n$. -->

@@

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure <$C1$ $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualization. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.
